The Spatial Relationship between Social Media, Digital Connectedness, and Social Isolation in China: Revisting Cyber-Optimism

### 2023-08-25 Social Isolation in China.qmd
Added residual plots and variable operationalizations.

library(tidyverse)
library(grid)
library(modelsummary)
library(scales)
library(papeR)
library(gridExtra)
library(knitr)
library(kableExtra)
library(ggthemes)
library(MASS)
library(sjPlot)

@@

More recent studies on the subject have found significantly more mixed and often negative evidence regarding the impact of social media on feelings of isolation. Primack et al. found a negative relationship between social media use and social isolation in youth in a representative sample [@primack2017]. A meta-review of the literature on adolescent social media usage notes that while the effect size is often small the relationship in most studies is negative [@valkenburg2022]. There are relatively fewer studies that consider all ages. However, those that have been conducted also generally find a negative (if modest) relationship [@appel2020]. More recent research has suggested that the effect of social media on measures like social isolation may be highly heterogeneous across individuals, a finding that would help reconcile some of the discrepancies in the literature [@beyens2020; @ostic2021].

@@

The most important of these contextual factor in China is that social media space that is highly controlled online environment. Many people are aware that the Chinese government heavily censors politically sensitive content on online platforms. However, fewer are aware that the Chinese government spends as much if not more effort to clean up non-political but negative or distressing content on the Chinese internet, such as scams, instances of cyber bullying, disturbing videos, and vulgar content [@wang2020]. This control impulse also extends content the government views as spiritually polluting, such as pornography, scantily dressed women, and other escapist content. While the Chinese government and online platforms are not 100 per cent effective in their ability to completely stamp out such content, the default is that such content is actively restricted, while US platforms tent to take a more pro-speech regulatory position [@liu2022]. If one of the main mechanisms through which social media promotes social isolation occurs is exposure to negative content, then this online environment should lead to a weaker relationship between social media use and isolation. Suggestive of this is a a study by Liu and Liu that finds those who consumed more commercialized and sensationalized media reported more trauma during the first COVID-19 in China than those who followed government sources [@liu2020].

@@

Aditionally, China's social media environment is relatively unique in that the dominant messaging platform is also the largest social media app (WeChat). Users can use it simply to chat with family and friends, they can use it to post photos and other content about their life in a feed that works similarly to Facebook, or they can browse videos of others in a method similar to Tiktok. Previous research has indicated that while, on the whole, social media increases social isolation, for users that primarily use it to contact friends and family, its use can counteract the negative effects [@hajek2019; @lim2020]. Given the ubiquity of WeChat in China, we expect to find similar results.

@@

Our contribution here is that we look at some well-established theoretical arguments in a context outside that of where most of the research centered on these type questions has examined. While our study is far from the last word on the subject, these results suggest that the mechanisms that link social media use and social isolation are relatively context-insensitive.

@@

@@

>>>>

library(tidyverse)
library(grid)
library(modelsummary)
library(scales)
library(papeR)
library(gridExtra)
library(knitr)
library(kableExtra)
library(ggthemes)
library(MASS)
library(sjPlot)
library(ggResidpanel)

@@

More recent studies on the subject have found significantly more mixed and often negative evidence regarding the impact of social media on feelings of isolation. Primack et al. found a negative relationship between social media use and social isolation in youth in a representative sample [@primack2017]. A meta-review of the literature on adolescent social media usage notes that while the effect size is often small the relationship in most studies on social media's linkage to ill-being is negative [@valkenburg2022] while emphasizing the importance of heterogeneous effects. There are relatively fewer studies that consider all ages. However, those that have been conducted also emphasize that the relationship between social media use and well-being has possible negative effects but the effects seem to vary by personality type [@appel2020]. More recent research has reinforced the finding that the effect of social media on measures like social isolation may be highly heterogeneous across individuals [@beyens2020; @ostic2021].

@@

The most important of these contextual factor in China is that social media space that is highly controlled online environment. Many people are aware that the Chinese government heavily censors politically sensitive content on online platforms. However, fewer are aware that the Chinese government spends as much, if not more, effort to clean up non-political as negative or distressing content on the Chinese internet, such as scams, instances of cyber bullying, disturbing videos, and vulgar content [@wang2020]. This control impulse also extends content the government views as spiritually polluting, such as pornography, scantily dressed women, and other escapist content. While the Chinese government and online platforms are not 100 per cent effective in their ability to completely stamp out such content, the default is that such content is actively restricted, while US platforms tent to take a more pro-speech regulatory position [@liu2022]. If one of the main mechanisms through which social media promotes social isolation occurs is exposure to negative content, then this online environment should lead to a weaker relationship between social media use and isolation. Suggestive of this is a a study by Liu and Liu that finds Chinese who consumed who consumed more commercialized and sensationalized media reported more trauma during the first COVID-19 outbreak in China than those who followed government sources [@liu2020].

@@

Additionally, China's social media environment is relatively unique in that the dominant messaging platform is also the largest social media app (WeChat). Users can use it simply to chat with family and friends, they can use it to post photos and other content about their life in a feed that works similarly to Facebook, or they can browse videos of others in a method similar to Tiktok. Previous research has indicated that while, on the whole, social media increases social isolation, for users that primarily use it to contact friends and family, its use can counteract the negative effects [@hajek2019; @lim2020]. Given the ubiquity of WeChat in China, we expect to find similar results.

@@

Our contribution here is that we look at some well-established theoretical arguments in a context outside that of where most of the research centered on these type questions has examined. While our study is far from the last word on the subject, these results suggest that the mechanisms that link social media use and social isolation are relatively consistent across countries.

@@

SES is an additive index of these two questions regarding income and education. Each of the following questions were rescaled to range from 0 through 1, then the two questions were summed, and then rescaled to range from 0 through 1 again.

-   Here is a table showing the range of monthly incomes that people have. Which of the letters on this table best represents the total monthly income of your household (after tax)?

    -   0 - 3,000,

    -   3,000 - 6,000,

    -   6,000 - 10,000,

    -   10,000 - 15,000,

    -   15,000 - 25,000,

    -   25,000 - 40,000,

    -   More than 40,000

-   What is the highest level of education that you have obtained?

    -   No formal education,

    -   Primary,

    -   Middle school,

    -   High school,

    -   University,

    -   Advanced Studies/Graduate School

Other important predictor variables are operationalized as follows:

-   Gender

    -   0 = male,

    -   1 = female

-   Are you a member or probationary member of the CCP?

    -   0 = no,

    -   1 = yes

-   How old are you? (rescaled to range from 0 through 1)

{{< pagebreak >}}

@@

```{r}
#| label: fig-resids-human
#| fig-cap: "Human Interaction Model Residuals"

resid_panel(mod5, plots = "R")
```

```{r}
#| label: fig-resids-online-offline
#| fig-cap: "Online/Offline Model Residuals"

resid_panel(mod6, plots = "R")
```
